Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-12 eswc-2012/phdsymp.tex
comment
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@66 43ef1190-90fd-4dd7-a769-d0121f02b80e
histograms grow large
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@67 43ef1190-90fd-4dd7-a769-d0121f02b80e

This problem has already received some attention, \cite{5337556}
addressed this problem by making it possible to exchange histograms,
but I suspect this will prove to become untenable as the number of
histograms to be computed and the number of bins in each histogram to
represent highly heterogenous data would be very high. This would also
cause the amount of statistical data to be exchanged between endpoints
to be very high.

@@

>>>>

This problem has already received some attention, \cite{5337556}
addressed this problem by making it possible to exchange histograms
and other data. However, histogram approaches generally suffers from
the problem that they grow too large or become a insufficiently
accurate digest, especially in face of very heterogenous data.

@@

\cite{Harth:2010:DSO:1772690.1772733} introduced QTrees to alleviate
the problem, but it is not clear to me if it will solve it.
